FlowFPX: Nimble Tools for Debugging Floating-Point Exceptions

### 2024-05-31 paper.tex
Clear preamble
Bump
Whedon does not like pifont it seems
cite p3109 wg report
flowfpx landing site link

% JuliaCon proceedings template
\documentclass{juliacon}
\setcounter{page}{1}
\usepackage{amsmath}
\usepackage{cleveref}
\usepackage{microtype}
\usepackage{pifont}

@@

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\FlowFPX}{FlowFPX}
\newcommand{\GPUFPX}{GPU-FPX}
\newcommand{\FloatTracker}{FloatTracker}
\newcommand{\FT}{\FloatTracker}
\newcommand{\Fp}{Floating-point} % hyphen or no?
\newcommand{\fp}{floating-point} % hyphen or no?
\newcommand{\CSTG}{stack graph}
\newcommand{\CPP}{\code{C++}}
\newcommand{\Dendro}{\textsc{Dendro}}
\newcommand{\urlaccess}[2]{\url{#1}}
\newcommand{\Nan}{\code{NaN}}
\newcommand{\NaN}{\Nan}
\newcommand{\Inf}{\code{Inf}}
\newcommand{\zerowidth}[1]{\makebox[0pt][l]{#1}}
\newcommand{\zerocode}[1]{\zerowidth{\code{#1}}}
\newcommand{\genpropkill}{\emph{gen}-\emph{prop}-\emph{kill}}
\newcommand{\bigcheckmark}{\ding{51}}
\newcommand{\bigxmark}{\ding{53}}
\newcommand{\tblnext}{\(\Rightarrow\)}
\newcommand{\tblY}{\mbox{\bigcheckmark}}
\newcommand{\tblN}{\scalebox{0.8}{\bigxmark}}

@@

@@

\Fp{} numbers use a finite number of bits to represent a spectrum of points along the real number line~(\cref{f:real-vs-fp}).
The implementation strategy is essentially that followed in scientific notation.
A \fp{} number packs a sign bit, an exponent, and a fraction part (also called the ``significand'' or ``mantissa'') into a bitstring.
Typical strings are 64 or 32 bits long, but 16-bit and 8-bit formats are on the rise~\cite{klowerLowprecisionClimateComputing2021,fp8}.
This representation supports very small and very large numbers in a narrow range of bits:

@@

>>>>

% JuliaCon proceedings template
\documentclass{juliacon}
\setcounter{page}{1}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cleveref}
\usepackage{microtype}
% \usepackage{pifont}

@@

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\FlowFPX}{FlowFPX}
\newcommand{\GPUFPX}{GPU-FPX}
\newcommand{\FloatTracker}{FloatTracker}
\newcommand{\FT}{\FloatTracker}
\newcommand{\Fp}{Floating-point} % hyphen or no?
\newcommand{\fp}{floating-point} % hyphen or no?
\newcommand{\CSTG}{stack graph}
\newcommand{\CPP}{\code{C++}}
\newcommand{\Dendro}{\textsc{Dendro}}
\newcommand{\urlaccess}[2]{\url{#1}}
\newcommand{\Nan}{\code{NaN}}
\newcommand{\NaN}{\Nan}
\newcommand{\Inf}{\code{Inf}}
\newcommand{\zerowidth}[1]{\makebox[0pt][l]{#1}}
\newcommand{\zerocode}[1]{\zerowidth{\code{#1}}}
\newcommand{\genpropkill}{\emph{gen}-\emph{prop}-\emph{kill}}
\newcommand{\bigcheckmark}{\ding{51}}
% \newcommand{\bigxmark}{\ding{53}}
\newcommand{\tblnext}{\(\Rightarrow\)}
% \newcommand{\tblY}{\mbox{\bigcheckmark}}
% \newcommand{\tblN}{\scalebox{0.8}{\bigxmark}}
\newcommand{\tblY}{\checkmark}
\newcommand{\tblN}{\scalebox{1.2}{$\times$}}

@@

\noindent%
The toolkit is online: \url{https://utahplt.github.io/flowfpx}

@@

\Fp{} numbers use a finite number of bits to represent a spectrum of points along the real number line~(\cref{f:real-vs-fp}).
The implementation strategy is essentially that followed in scientific notation.
A \fp{} number packs a sign bit, an exponent, and a fraction part (also called the ``significand'' or ``mantissa'') into a bitstring.
Typical strings are 64 or 32 bits long, but 16-bit and 8-bit formats are on the rise~\cite{klowerLowprecisionClimateComputing2021,fp8,p3109}.
This representation supports very small and very large numbers in a narrow range of bits:

@@

\bigskip
